We propose \ldjoins, a new approach to reduce the computational cost of RDF query processing.
In \ldviews

to support web portal applications that use massive RDF datasets.
Our approach pre-computes the join operations needed in the queries to support the web portal, and indexes the resulting data so that no join operations are performed at query time.
We use the JSON-LD serialization of RDF \cite{Lanthaler:2012:UJC:2307819.2307827} to index the data in a NoSQL store, and enable clients to query the RDF using the native query language of the NoSQL store.

In section~\ref{sec:motivation} we present a taxonomy of the types of queries needed in Web portals and discuss how these queries can be combined to build web portals in a variety of domains.
We present details of our approach in section~\ref{sec:approach}, including a formal definition of the types of queries we propose to support, the approach for specifying and pre-computing joins, and the approach to indexing the data in ElasticSearch, the NoSQL store we use in our implementation.
We evaluate our approach in section~\ref{sec:evaluation}, describing a new benchmark for evaluating query performance for web portal applications. 
Our evaluation shows that our approach vastly outperforms centralized SPARQL and Linked Data Fragments, enabling 1 second response times in a large web portal compared to XXX seconds in SPARQL and YYY seconds in Linked data Fragments.
We compare our work with other approaches in section~\ref{sec:related-work} and close with a discussion of the results and directions for future work in section~\ref{sec:discussion}.
